\section{Dynamic Screening and UOT problem}
\subsection{Screening for UOT}

For UOT problem \ref{eq:uot}, we could get its dual form. 
\begin{lem}(Dual form of UOT problem)
\begin{equation}
\begin{split}
-d^*(-\theta) - g^*(X^{\tranT}\theta)& = -\frac{1}{2}\|\theta\|_2^2-y^{\tranT}\theta \\
 \mathbf{s.t.} \quad \forall i \quad x_i^{\tranT}\theta -\lambda c_i &\leq 0
 \end{split}
 \label{eq:uotdual}
\end{equation}
\end{lem}
The equation indicate a dual feasible area constructed by many dual constraints, the optimal solution is inside the constraints.\\
From the KKT condition, we can make sure that, for the optimal primal solution $\hat{t}$:
\begin{thm} (Screening) For the dual optimal solution $\hat{\theta}$, we have the following relationship:
 \begin{equation}
\begin{split}
x_i^{\tranT}\hat{\theta} -\lambda c_i  \left\{
\begin{aligned}
< 0 \quad& \Rightarrow \hat{t}_i = 0\\
= 0 \quad& \Rightarrow \hat{t}_i \geq 0
\end{aligned}
\right.
 \end{split}
 \label{eq:screening}
\end{equation}
\end{thm}

As we do not know the information of $\hat{t}$ directly, we can construct an area $\mathcal{R}^{S}$ containing the $\hat{t}$, if

 \begin{equation}
\max_{t \in \mathcal{R}^S} x_i^{\tranT}\theta -\lambda c_i  < 0
\end{equation}
then we have:
 \begin{equation}
 x_i^{\tranT}\hat{\theta} -\lambda c_i  < 0
\end{equation}
which means the corresponding $\hat{t}_i = 0$, and can be screening out.

Now we start to construct the area containing $\hat{\theta}$, from \ref{circle} we know that the $\hat{\theta}$ is inside the intersection of the area of \ref{circle} and the dual feasible area. However, the multilinear constraints make it hard to compute the maximum for the problem, We design a relaxation method. which divide the constrains into two parts, then we are maximizing on the intersection of two hyperplane and a hyper-ball. 

\begin{thm}\label{area}
$$
\mathcal{R}^S = \{ nihao \}
$$
\end{thm}
the computational process is in Appendix.A

\subsection{Screening Algorithms}

 \begin{algorithm}
 \caption{UOT Dynamic Screening Algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE $t_0, S \in R^{n\times m}, S_{ij}=1$
 \ENSURE  $S$
  \STATE \text{Choose a solver for the problem.}
  \FOR {$t = 0 \text{ to } K$}
  \STATE $\text{Projection } \tilde{\theta} = \operatorname{Proj}(t_k)$ 
  \IF {($i \ne 0$)}
  \STATE $\textbf{break}$
  \ENDIF
    \STATE $\mathcal{R} \Leftarrow \mathcal{R}^S{(\tilde{\theta},t_k)}$
    \STATE $S \Leftarrow {S_{ij} = 0 \text{ if } \max_{\theta \in \mathcal{R}^S} {x_{k(i,j)}}^{\tranT}\theta <\lambda c_{k(i,j)} }$
    \FOR {$a  \in {A_{ij}\|A_{ij}=0}$}
    \STATE $t_k(i,j) \Leftarrow 0$
    \ENDFOR
    \STATE $t_{k+1} = \operatorname{update}(t_k)$
  \ENDFOR
  
 \RETURN $t_{K+1}, S $ 
 \end{algorithmic} 
 \end{algorithm}

screening method is irrelevent to the optimization solver you choose. We gave the specific algorithm for $L_2$ UOT problem to show the whole optimization process.\\
An important part is that we use the primal solution to compute a dual solution, which might not inside the dual feasible area, a projection method is necessary. We promote a new projection method for the UOT problem for its sparse matrix structure.

\begin{thm}\label{proj}
$$
\tilde{\theta} = 1
$$
\end{thm}











































