\section{Introduction}
Optimal Transport (OT) has a long history in mathematics and prevailed recently due to its important role in measuring the distance between histograms in the Machine Learning community. It outperforms the traditional method in many fields like domain adaptation \citep{7586038}, generative model \citep{arjovsky2017wasserstein}, graph machine learning \citep{NEURIPS2019_fdd5b16f} and natural language processing. \citep{084adf2f555549c493e0331a00e4ecad} Its popularity is attributed to the introduction of the Sinkhorn algorithm to the entropic optimal transport problem, \citep{NIPS2013_af21d0c9} which improved the computational speed of OT problem from $\Theta (n^3)$ of Simplex method to $\Theta (n^2)$. However, Optimal transport problem can only deal with balanced samples, which limits its application in various data structures. Unbalanced Optimal Transport (UOT) problem has been promoted to deal with the drawback on unbalanced samples. Traditional Sinkhorn method can deal with an entropic UOT problem as well, but suffered from the slow convergence rate of the large penalty part and a non sparse solution, It can also be solved with other methods like Majorization-Minimization and FISTA method according to the choice of the penalty function in the primal problem and the Lagrange method for dual problem\citep{NEURIPS2021_c3c617a9}. UOT problem has a similar structure with many other famous problems like Non-negative Matrix Factorization and Lasso problem, which encourage the researchers to use the abundant results in these field to improve it.

Screening is a famous method in Lasso problem field, the $L_1$ penalize function causes a sparse solution for problem, which constrains many elements of solution equal to zero. The large scale optimization problem suffers from the computational process for manipulating on these zeros elements. \citep{ghaoui2010safe} invented the safe screening, which could theoretically judge whether the elements in solution equal to zero. It freezed the identified elements with linear complexity computation and save optimization time. Many new methods have been promoted to revise the method, \citep{JMLR:v18:16-577} invented the dynamic screening to dynamically screening out zeros elements, and there are many paper tries to improve it.  

Fortunately, the OT function in UOT problem has the same effectiveness as $L_1$ in lasso and cause a sparse solution. We believe that this method could be applied on UOT problem and have better performance than ordinal Lasso problem for its special structure.

\textbf{Contribution}: 
\begin{itemize}
\item We systematically combine the framework of Screening method on UOT problem, and we give a correct projection method for UOT screening, which is better than the Lasso one. 
\item We also imporve the constraints construction method for the specific sparse structure of UOT problems and benefits from it.
\end{itemize}



